\chapter*{ACKNOWLEDGEMENT}

\begin{acknowledgements}
\newcommand{\tab}{\hspace*{2em}}

\hspace{0.75cm}At the outset, we would like to thank the Almighty for all his blesssings that led us here. %His stimulating suggestions and encouragement helped me in all the time of my research and writing of this thesis. 
%I express my heart-felt gratitude to  my  guide, \emph{Mr. Syed Farook K.}, Assistant Professor, for his committed guidance, valuable suggestions, and constructive criticisms, and support  throughout the work. 

We are grateful to \emph{\textbf{Dr. Rahumathunza I}, Principal, MES College of Engineering, Kuttippuram}, for providing the right ambiance to complete this project. We would also like to extend our sincere gratitude to \emph{\textbf{Dr. Govindaraj E}, Associate Professor, Head of Department,  Artificial Intelligence and Data Science, MES College of Engineering, Kuttippuram.}

We are deeply indebted to the project coordinator, \emph{\textbf{Mr. Sherikh K K}, Assistant Professor, Department of Artificial Intelligence and Data Science} for his continued support.

It is with great pleasure that we express our deep sense of gratitude to our project guide, \emph{\textbf{Ms. Vishnupriya M V}, Assistant Professor,  Department of Artificial Intelligence and Data Science}, for her guidance, supervision, encouragement and valuable advice in each and every phase.

We would also like to express our sincere thanks and gratitude to all staff members of the department, our friends and family members for their cooperation, positive criticism, consistent support and consideration during the preparation of this work.
\vspace{1cm}
\begin{center}





        SAINABA SHAHANAS K.K \\
	

    
    
    
    
\end{center}



\end{acknowledgements}