\addtocontents{toc}{\cftpagenumbersoff{chapter}}
\titlespacing*{\chapter}{0pt}{-30pt}{10pt}

%\chapter*{References}\label{References}
%  \markboth{References}{}
  
%  \addcontentsline{toc}{chapter}{References}
%  \label{page:References}
\bibliographystyle{IEEEtran}
% \bibliographystyle{plain}	% or "siam", or "alpha", or "abbrv"
				% see other styles in
				% /usr/local/TeX/texmf/bibtex/bst

\nocite{*}		        % list all refs in database, cited or not.

	% bib database in "seminar.bib"

\begin{thebibliography}{99}


\bibitem{key1} Y. Zhen, J. -D. Luo and H. Chen,
 \newblock{"Prediction of Academic Performance of Students in Online Live Classroom Interactions—An Analysis Using Natural Language Processing and Deep Learning Methods,"} 
  \newblockInternational in\textit{ Journal of Social Computing}, vol. 4, no. 1, pp. 12-29, March 2023, doi: 10.23919/JSC.2023.0007.

\bibitem{key2} Gupta, Swadha & Kumar, Parteek & Tekchandani, Raj.
 \newblock{”Facial emotion recognition based real-time learner engagement detection system in online learning context using deep learning models.”,}
  \newblockInternational \textit{Multimedia Tools and Applications.} 82. 10.1007/s11042-022-13558-9. 
 
\bibitem{key3} Fahd, Kiran & Miah, Shah & Ahmed, Khandakar. (2021).
 \newblock{”Predicting student performance in a blended learning environment using learning management system interaction data.”,}
  \newblockInternational \textit{Applied Computing and Informatics.} ahead-of-print. 10.1108/ACI-06-2021-0150. 
  
\bibitem{key4}  Mrhar, Khaoula & Benhiba, Lamia & Bourekkache, Samir & Abik, Mounia. (2021).
 \newblock {“ A Bayesian CNN-LSTM Model for Sentiment Analysis in Massive Open Online Courses MOOCs.“,}
  \newblockInternational \textit{International Journal of Emerging Technologies in Learning (iJET)}. 16. 216-232. 10.3991/ijet.v16i23.24457. 

\bibitem{key5}  Nezami, O.M., Dras, M., Hamey, L., Richards, D., Wan, S., & Paris, C. (2018).
 \newblock{” Automatic Recognition of Student Engagement Using Deep Learning and Facial Expression”,}
  \newblockInternational \textit{ECML/PKDD} (2018).

\bibitem{key6}Alyuz, Nese & Okur, Eda & Oktay, Ece & Genc, Utku & Aslan, Sinem & Mete, Sinem & Arnrich, Bert & Esme, Asli. (2016).
\newblock {“ Semi-supervised model personalization for improved detection of learner's emotional engagement“,}
\newblockInternational \textit{100-107. 10.1145/2993148.2993166. }


\bibitem{key7}Bosch, Nigel. (2016).
\newblock {“Detecting Student Engagement: Human Versus Machine“,}
\newblockInternational  317-320. 10.1145/2930238.2930371.


\bibitem{key8}Bosch, N., D’Mello, S.K., Ocumpaugh, J.L., Baker, R., & Shute, V.J. (2016).
\newblock {“ Using Video to Automatically Detect Learner Affect in Computer-Enabled Classrooms”,}
\newblockInternational \textit{ACM Trans. Interact. Intell. Syst}., 6, 17:1-17:26.

\bibitem{key9}Blanchard, Nathaniel & Bixler, Robert & Joyce, Tera & D’Mello, Sidney. (2014).
\newblock {“Automated Physiological-Based Detection of Mind Wandering during Learning.“,}
\newblockInternational 8474. 10.1007/978-3-319-07221-\_7. 

\bibitem{key10}H. Monkaresi, N. Bosch, R. A. Calvo and S. K. D'Mello,
\newblock {"Automated Detection of Engagement Using Video-Based Estimation of Facial Expressions and Heart Rate,"}
\newblockInternational in \textit{IEEE Transactions on Affective Computing,} vol. 8, no. 1, pp. 15-28, 1 Jan.-March 2017, doi: 10.1109/TAFFC.2016.2515084.

\bibitem{key11}J. Whitehill, Z. Serpell, Y. -C. Lin, A. Foster and J. R. Movellan,
\newblock { "The Faces of Engagement: Automatic Recognition of Student Engagementfrom Facial Expressions,"}
\newblockInternational in\textit{ IEEE Transactions on Affective Computing,} vol. 5, no. 1, pp. 86-98, 1 Jan.-March 2014, doi: 10.1109/TAFFC.2014.2316163.


\bibitem{key12}Baker, Ryan & Corbett, Albert & Koedinger, Kenneth & Wagner, Angela. (2004).
\newblock {” Off-Task Behavior in the Cognitive Tutor Classroom: When Students "Game The System".“,}
\newblockInternational Conference on Human Factors in Computing Systems - Proceedings. 383-390. 10.1145/985692.985741.


%\bibitem{key6}D. J. Brown and M. J. Proulx,
 %\newblock\textit{"Audio–Vision Substitution for Blind Individuals: Addressing Human Information Processing Capacity Limitations",}
  %\newblockInternational   IEEE Journal of Selected Topics in Signal Processing, 2016.
%\bibitem{key7} Ryan Kiros, Ruslan Salakhutdinov, and Rich Zemel,
 %\newblock\textit{"Multi modal neural language models",}
  %\newblockInternational in Proceedings of' the 3ist international Conference on Machine Learning (iCML-i4), 2014.
%\bibitem{key8}Y.Feng and M. Lapata,
 %\newblock\textit{""Automatic Caption Generation for News Images",}
  %\newblockInternational   IEEE Transactions on Pattern Analysis and Machine Intelligence, 2013.
%\bibitem{key9} Donggeun Yoo, Sunggyun Park, Joon-Young Lee, and In Kweon,
 %\newblock\textit{"Multiscale pyramid pooling for deep convolutional representation",}
  %\newblockInternational  in Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition Workshops, 2015.  
 
 




%\bibitem[Label1, 2011]{key5}[5] Tapaliana Bhattasali,Rituparna Chaki,Sugata Sanyal
% \newblock "Sleep Deprivation Attack Detection in Wireless Sensor Networks",
% \newblock \emph{International journal of computer applications(0975-8887)vol 40- No: 15,February 2012 }
 
% \bibitem[Label1, 2011]{key6}[6] Eugene Y. Vasserman, Nicholas Hopper,
% \newblock " Vampire Attacks: Draining Life from Wireless Ad Hoc Sensor Networks",
% \newblock \emph{IEEE transactions on mobile computing, VOL. 12, NO. 2, February 2013 }
 
%  \bibitem[Label1, 2011]{key7}[7] Yazeed Al-Obaisat,Robin Braun,
% \newblock "On Wireless Sensor Networks: Architectures,Protocols,Applications and Management",
% \newblock \emph{Institute of Information and Communication Technologies,May 2004 }
  
\end{thebibliography}